Title: Reduced plasticity and variance in physiological rates of ectotherm populations under climate change

### 2024-03-12 ms.qmd
MS updated. Need to format for Sci Advances now
Updating formatting for figs so they are bold and Fig.

---
title: "Title: Reduced plasticity and variance in physiological rates of ectotherm populations under climate change"
bibliography: ./bib/refs.bib
csl: ./bib/science-advances.csl
format:
  docx:
    reference-doc: ./bib/template.docx
editor_options: 
  chunk_output_type: console
execute:
  freeze: auto  # re-render only when source changes
  cache: false
  echo: false
  warning: false
  error: false
  include: true
crossref:
  fig-title: 'Figure'
  fig-labels: arabic
  title-delim: "-"
  fig-prefix: "Figure"
  tbl-prefix: "Table"
---

@@

## Authors: <p style="text-align: center;">Daniel W.A. Noble^1^ $\ddagger$, Fonti Kar^2^,  Alex Bush^4^, Frank Seebacher^3^ $\dagger$, & Shinichi Nakagawa^2^ $\dagger$</p>

>>>>

---
title: "Title: Reduced plasticity and variance in physiological rates of ectotherm populations under climate change"
bibliography: ./bib/refs.bib
csl: ./bib/science-advances.csl
format:
  docx:
    reference-doc: ./bib/template.docx
editor_options: 
  chunk_output_type: console
execute:
  freeze: auto  # re-render only when source changes
  cache: false
  echo: false
  warning: false
  error: false
  include: true
crossref:
  fig-title: '**Fig.**'
  fig-labels: arabic
  title-delim: "-"
  fig-prefix: "**Fig.**"
  tbl-prefix: "Table"
---

@@

## Authors:

 <p style="text-align: center;">Daniel W.A. Noble^1^ $\ddagger$, Fonti Kar^2^,  Alex Bush^4^, Frank Seebacher^3^ $\dagger$, & Shinichi Nakagawa^2^ $\dagger$</p>
